Structured Versus Decorated Cospans

### 2022-04-18 cospans_compositionality_4.tex
perhaps all errors are fixed... there's one sentence Christina found confusing.

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/04/16 - 4th version sent to Compositionality: version for publication - fixing mistakes

@@

In \cref{DecCospansDoubleCat} we construct the double category of decorated cospans, $F\lCsp$, and show how to construct maps between decorated cospan double categories. In \cref{Structured} we give a new construction of the double category of structured cospans, ${}_L \lCsp(\X)$.  In \cref{EquivDoubleCats} we prove that the double categories of decorated cospans and structured cospans are isomorphic under suitable conditions.  In \cref{spinoffs} we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).  In \cref{Applications} we describe applications, and show that open dynamical systems can be described using decorated cospans but not structured cospans.

@@

In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.   However, in \cref{subsec:petrirates} we describe a map from open Petri nets with rates to open dynamical systems.  The former are conveniently described using structured cospans, while the latter can only be treated using decorated cospans.   Here \cref{thm:equiv} serves as a bridge that lets us connect the two formalisms.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/04/18 - 4th version sent to Compositionality: version for publication - fixing mistakes

@@

In \cref{DecCospansDoubleCat} we construct the double category of decorated cospans, $F\lCsp$, and show how to construct maps between decorated cospan double categories. In \cref{Structured} we give a new construction of the double category of structured cospans, ${}_L \lCsp(\X)$.  In \cref{EquivDoubleCats} we prove that the double categories of decorated cospans and structured cospans are isomorphic under suitable conditions.  In \cref{spinoffs} we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).  In \cref{Applications} we describe applications.

@@

In some cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.  However, in some cases decorated cospans appear to be necessary, and in \cref{subsec:petrirates} we explain why \cref{thm:equiv} does not apply to open dynamical systems.
